Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-15 rnni_convexity.tex
hide keys
refs for cluster representation + MBIE expanded

Before introducing the algorithm we need the following definitions.
Each node $v$ of a tree defines a \emph{cluster} $C$, which is the set of taxa descending from $v$.
We then say that $v$ \emph{induces} $C$.
All trees on $n$ leaves share trivial clusters, which are those induced by leaves and the root, so we exclude them from consideration and say cluster to mean a non-trivial cluster.
A tree in unambiguously defined by the list of its clusters sorted according to the rank of the inducing nodes.
We will refer to this list of $n-2$ clusters for a given tree on $n$ taxa as a \emph{cluster representation} of the tree.

@@

We acknowledge support from the Royal Society of New Zealand through the Rutherford Discovery Fellowship awarded to AG.
This work was partially supported by MBIE through the Endeavour Smart Ideas and Data Science Programmes grants.

>>>>

Before introducing the algorithm we need the following definitions.
Each node $v$ of a tree defines a \emph{cluster} $C$, which is the set of taxa descending from $v$.
We then say that $v$ \emph{induces} $C$.
All trees on $n$ leaves share trivial clusters, which are those induced by leaves and the root, so we exclude them from consideration and say cluster to mean a non-trivial cluster.
A tree in unambiguously defined by the list of its clusters sorted according to the rank of the inducing nodes.
We will refer to this list of $n-2$ clusters for a given tree on $n$ taxa as a \emph{cluster representation} of the tree \autocite{Gavryushkin2018-ol, Gavryushkin2016-uu, Semple2003-nj}.

@@

We acknowledge support from the Royal Society of New Zealand through the Rutherford Discovery Fellowship awarded to AG.
This work was partially supported by the Ministry of Business, Innovation, and Employment of New Zealand through the Endeavour Smart Ideas and Data Science Programmes grants.
